Demo: Counterpoint by Construction

### 2019-06-25 doc/farm/farm-abstract.tex
minor fixes

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
We present \emph{Music Tools}, an Agda library for analyzing 
and synthesizing music.  
The library uses dependent types to simplify encoding of 
music rules, thus improving existing approaches based on 
simply typed languages.  
As an application of the library, we demonstrate an 
implementation of first-species counterpoint, where we use
dependent types to constrain the motion of two parallely
sounding voices.
\end{abstract}

@@

The last requirement is that the music must end with a cadence,
which is a final motion from the 2nd or 7th degree to the tonic 
(1st degree). 
We impose this requirement by declaring two cadence constructors 
as the base cases of counterpoint (note that the final interval of
the cadence is always \texttt{(p, per8)} and is thus not explicitly
specified).
Thus, we arrive at the following datatype for well-typed counterpoint\footnote{
For readability, we have omitted explicit conversions 
from \texttt{PitchInterval} (which ensures the interval is not dissonant) 
to the general \texttt{Interval}.}.

@@

For counterpoint specifically, we plan to represent higher species 
counterpoint by extending the rules, 
and to explore automatic generation of species counterpoint.
It would be interesting to compare our correct-by-construction counterpoint
and one created by machine learning \citep{CounterpointByConvolution}, 
which does not have correctness guarantees.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
We present \emph{Music Tools}, an Agda library for analyzing 
and synthesizing music.  
The library uses dependent types to simplify encoding of 
music rules, thus improving existing approaches based on 
simply typed languages.  
As an application of the library, we demonstrate an 
implementation of first-species counterpoint, where we use
dependent types to constrain the motion of two parallel
voices.
\end{abstract}

@@

The last requirement is that the music must end with a cadence,
which is a final motion from the 2nd or 7th degree to the tonic 
(1st degree). 
We impose this requirement by declaring two cadence constructors 
as the base cases of counterpoint (note that the final interval of
the cadence is always \texttt{(p , per8)} and is thus not explicitly
specified).
Thus, we arrive at the following datatype for well-typed counterpoint\footnote{
For readability, we have omitted explicit conversions 
from \texttt{PitchInterval} (which ensures the interval is not dissonant) 
to the general \texttt{Interval}.}.

@@

For counterpoint specifically, we plan to represent higher species 
counterpoint by extending the rules, 
and to explore automatic generation of species counterpoint.
It would be interesting to compare our correct-by-construction counterpoint
with that created by machine learning \citep{CounterpointByConvolution}, 
which does not have correctness guarantees.
